### 2012-11-12 doc/progress_plan/report.tex
Added some diagrams to progress plan repository and updated gitignore to ignore swp files

\subsection{Introduction}
Partridge is a web-based tool designed to assist in information processing and knowledge
acquisition in the domain of scientific research.

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  A 2009 study by B-C
Bj\"{o}rk suggests that approximately 1.4 Million papers were published in the
year 2006 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines is providing researchers with an even larger volume
of information to be processed. As the amount of available information grows,
relevant material becomes increasingly difficult to find and the need for an
automated information retrieval tool is ever more apparent.

>>>>

\subsection{Introduction}
Partridge is a web-based tool designed to assist in information processing and knowledge
acquisition within the domain of scientific research.

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  A 2009 study by B-C
Bj\"{o}rk suggests that approximately 1.4 Million papers were published in the
year 2006 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing researchers with an even larger volume of information to be
processed. As available information increases, relevant material becomes
progressively more difficult to find and the need for an automated information
retrieval tool more apparent.
